% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}

% Please include a clear, concise, and descriptive title
\title{CPD Report}

% Please do not change the subtitle
\subtitle{COMP240 - CPD Report}

% Please put your student number in the author field
\author{1605240}

\begin{document}

\maketitle

\section*{Introduction}
The time has come, we are now at the end of our second year of university, only one more year left to go! This report highlights five key skills I feel I need to work on and how to improve on them. Sticking to trying to improve these skills will offer me a huge advantage as I tackle my bad habits. Looking bad at my last CPD I feel as if improved quite well on three of my key skills, the other two, not so much, some of the skills stem from those two I didn't improve on so I've broken them down further to see if that'll help.

\section{Making Progress On Work Early On}
This term I feel like I've been enjoying it more and managing to make good progress on my work, the issue with this is I, like many other students, I leave making lots of progress with my work until close to the deadline. In my ideal world I'd do bit by bit every week instead of only working on the assignment a few weeks until it is due. This plays a large role in the quality of my work as it leaves me less time to change it towards the end. I need to start doing work on every module at least once a week and try and make ANY progress I can. I normally use the first few weeks as learning time and don't do too much at home. In industry I'd fall way behind and get into lots of trouble. As mentioned above any progress is better than none, so next year I'm going to make it a goal of mine to make progress on every unit, every week.


\section{Mental Health}
This term I almost feel as if my mental health has regressed. This is something I don't really like speaking about but I believe it has played a massive role in the quality of my work this term. I don't want to get into too much details about it. I just need to make sure in the future I speak to living support and seek out the help I need to get. If I am able to do this I will be happier and less stressed. In the games industry I'd probably be forced to take time off of work which is not something I'd like to have to do.


\section{Challenging Myself}
Challenging myself is something I feel like I could improve on. This also fits together with making progress with my work early on. Towards the end of term I struggled with the AI and distributed systems modules until I spent enough time figuring out how to do it, by that time I was stressed at how little time I had left and decided to leave them at a level which I knew would get a pass. From there I should have challenged myself to push for a better mark, but due to time restrictions I left them. Even if I pushed myself a little bit it could go such a long way. In the games industry this wouldn't make me a good candidate for jobs because there are other people who would push for the best. To try and improve on this, as mentioned above I'm going to attempt to do work from every module every week and even if I make the smallest of progress it would still be a success.


\section{Communicating With the WHOLE Team}
Since I am a very introverted person I have had trouble communicating with my whole team. There are certain members which I can talk to and get along with easily, however in life there are always people you're not going to get along with. I managed to speak to most of my team but one or two members always made it difficult to talk to everyone because I believe they valued their own opinion too much. I have made it a goal of mine to be able to effectively communicate with the whole team so communication is top notch. If I did this in the games industry it would slow down progress on what ever was being worked on, and would lead to me getting into trouble. I realize this has to change so next year I've decided to try and talk to the whole team even if there are issues between people. I want development to go smoothly and this would help massively.


\section{Different Aspects Of Game Programming}
This year I have mainly focused on gameplay programming and AI programming within my team game. I would like to broaden my skill set and for next years development I'd like to try out different aspects of game programming, try things like UI programming and potentially things like level design. To relate this to the games industry it would give me a greater chance of getting a job with an idie studio which is something I'd like to do. If I were to relate this to a triple A studio they'd probably prefer me to specialize in one area which I'd like to focus on. To ensure I do this I'm going to take up small tasks next year in things I wouldn't normally do or watch my team members and see how they do.


\section*{Conclusion}
If I am able to follow all the steps listed above this will lead to me developing not only as a game developer but as a person which is something I believe everyone should always be striving to achieve. I want to make the most out of my degree while I am at university so in third year I'm going to try my hardest to do the best I can.
 

\bibliographystyle{ieeetran}
\bibliography{references}

\end{document}
