% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}

% Please include a clear, concise, and descriptive title
\title{CPD Report}

% Please do not change the subtitle
\subtitle{COMP230 - CPD Report}

% Please put your student number in the author field
\author{1605240}

\begin{document}

\maketitle

\section*{Introduction}
This term has flown by and we're already half way through university now, it's such a strange feeling but I'm glad I'm still here and learning every day. In this report I have identified five key skills from this term I need to improve on to better myself along with my learning. If I stick to these skills I believe it will benefit me massively as a developer and as an individual. Looking back at my last CPD I think I have improved quite well on three out of my five goals which I am proud of as sticking to goals is something I was never too good at.

\section{C++ Skills}
Although this was one of my goals from last year I don't think I got anywhere near to where I wanted to be with it. This term I haven't used as much C++ as I wanted to. This should change as you can do so much more with C++ than just using it in unreal, using it more will help further my development as a game programmer and programmer in general. To help me improve on my C++ by the end of Summer I want to have made my own game almost entirely using C++ and throughout the next term implement small features into my games which use C++ code. Since I have a better understanding of C++ and coding than I did last year hopefully it will be easier than before and I intend to stick to this goal now. Also to help me I will read more of the documentation and try and follow online tutorials to keep learning. By doing this it should up my quality of work all round. I will make small C++ side projects to help learn also. By doing all these steps it will help me become a more employable game developer.


\section{Motivation}
Motivation plays such a large part in life, the more motivated you are, the better things you tend to make and generally you are happier. In the games industry the more motivated you are the better work you produce and you usually end up with a better job. I feel my work is never the best it can be and that is due to my motivation dropping down sometimes, this makes me quite upset. To help myself keep motivation levels high I am going to plan out my time and set myself goals to follow every week, if I am successful then I will reward myself, otherwise I need to catch up on what I didn't do. This should help me keep focused and motivated to do my work. I really want this goal to work out for me due to how much it can help me with life in general.

\section{Not Asking For Help Last Minute}
One of my goals last year was to ask for help more when I was stuck, this year I feel I've been doing that but now I've realized I only ask last minute. This is no good as last minute there is usually no time for anyone to help me. If I did this in industry and couldn't manage to do my work I'd probably end up being fired or get into lots of trouble. This also effects my work in a big way as by the time I ask for help it's too late really for me to make a significant change to my work. To improve on this I plan on asking the lecturers more questions and asking them more frequently as they're not going to judge me, they're there to help. This should help me to make better work on a more consistent basis. To measure this I will try to stay up to date and understand all my current work at the time and if I don't I'll be sure to ask for help.


\section{Self Help}
This term I've come to realise mental health can play a major role in your life for the good and the bad things. Unfortunately I've been struggling with some personal issues of my own which at many points throughout the term which left my feeling extremely down and making my work not as good as I'd like because I feel I can't do anything when I'm like this. In industry if this happened I'd need to speak to someone immediately so they knew what was going on and how they could help. To help myself with these problems more in the future I need to speak to student support services early on when I start to feel like this because leaving it late does no good for me. I now know that they are there to help me and not to judge me. How I feel should be a higher priority in my life because after all I am here for me and no one else. To help me keep track of this I plan to start a diary of how I feel and the problems I encounter in my everyday life.


\section{Communicating With Others}
This is another goal from last year I wasn't 100 percent happy with my progress so far. I am a very good listener however my communicating skills aren't the best, they've improved and are still improving. Communication plays a vital role in game development and if I can't communicate there is no point trying to become a developer as it is a team job. When I learn to communicate better it will get my ideas out there too not just the teams one and help us deliver a better final product. To improve I will be more vocal during team meetings because I've learnt the worst they can say is no and if they like my ideas it could add so much more to our game. To measure this I hope to see an improvement in my peer review feedback for our team game. This can be done instantly and can make a big difference.


\section*{Conclusion}
Throughout this report I have documented what I think are the five key skills I should improve on and have suggested goals and aims to help me reach this stage. By following these goals it should help me become a better programmer, game developer and lead a happier and less stressful life which is my main aim in the end. By the end of the year I want to leave satisfied with the work I hand in at the end of the next term. On top of all this I need to keep up with my other skills I highlighted last year and keep up with them, this is why I am going to start planning out my weeks to make sure I keep on top of all my work. I now realise how useful these reports can be and how many skills I just leave at an unsatisfactory level.


\bibliographystyle{ieeetran}
\bibliography{references}

\end{document}
